---
title: "Player Analysis Workflow"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{player_comparison_vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(NBAplayRs)
```

The purpose of the NBAplayRs package is to help others measure individual performance in the NBA and compare their regular and post season performance.

This is a difficult challenge as there is a lot of confounding factors while trying to measure performance, such as where the game was played, the player who is guarding them, who is on the court from their team, who is on the court from the opposing team, and more. This package utilizes a known metric VORP. This can then be further used to calculate the adjusted VORP of an individual.

Adjusted VORP is calculated to get rid of all various effects and measure an individual's performance. 

## NBAplayRs Workflow Overview
1. Reading in the Data
2. Gathering the Data
3. Cleaning the Data
4. Measuring Two Player's Performances
5. Seeing How a Team Performed Over a Season


## Reading in the Data
The first step of measuring performance is by reading in the required data of games. Fortunately, these have been already added into the package. Hence, no reading in is actually required. For an overview of the data added, here is a few rows.
```{r}
head(regular_season)
```

There is the data of all recorded regular season games and post season games in this package. 

## Gathering the Data
The next step is gathering the data. The data for NBA players can be found on www.basketballreference.com, which will be used in this package. There are a lot of functions that need to be used prior to gathering the data from the website though.

```{r}
names(regular_season) <- names
my_list <- list()
reg.80 <- filter_teams1(1980,1990,regular_season,'BOS','DET','LAL')
boston.80 <- cleaning(reg.80,'BOS',my_list)
```

These two functions clean up all of the games to specific times and teams. This makes the webscraping more manageable. Next, the VORP is calculated while webscraping. For this example, only one data point will be used as this can be very computational challenging and time consuming. 

```{r}
boston <- vorp(boston.80[[1]][1:2,])
head(boston)
```


## Cleaning the Data
The next step is cleaning the data that was gathered. The adjusted VORP of the year can be calculated with another function in the package.
```{r}
bind(boston, 1985, 'BOS-1985', 'regular')
```

## Measuring Two Player's Performances
This is then done for various years and all bound into a single dataframe called Celtics, which is another provided dataframe in the package. Additionally, there are various other teams for specific years provided. 

## Seeing How a Team Performed Over a Season


